p-adic stability in linear algebra

### 2015-01-09 examples/stability.tex
Figure for the table of benchmarks for LU

\noindent
{\bf Numerical experiments.}
\todo{Do it.}

>>>>

\noindent
{\bf Numerical experiments.}
Let $B_n=(E_{i,j})_{1 \leq i,j\leq n}$ be the canonical basis of 
$M_n(K)$. It can be naturally seen as a basis of $L_n \times U_n$ as
well. For a given $M \in O_n$, let us abuse notation and write $D'(M)$
for the matrix of this linear mapping in the above basis. We remark that
$D'(M)$ is lower-triangular in this basis. Projecting $D'(M)$ onto each
coordinate, we find the best coordinate-wise loss of precision we can 
hope for the computation of $D$ is given by $\sum_u \left( \max_v \left( 
val(D'(M)_{u,v}) \right) \right)$. This number should be compared to
$val(\det(D'(M)))$, which is the lattice-method loss of precision.
Figure \ref{fig:LU} sums up the mean and standard deviation of those 
losses for a sample of 2000 random matrices in $M_d(\mathbb{Z}_2)$.
%
\begin{figure}
\begin{center}
\renewcommand{\arraystretch}{1.2}
\begin{tabular}{|c|c|c|c|c|}
\hline 
& \multicolumn{4}{|c|}{Loss of precision} \\
\cline{2-5}
\raisebox{0.2em}{matrix}
& \multicolumn{2}{|c|}{coord-wise method} & \multicolumn{2}{|c|}{lattice method}  \\  \cline{2-5}
\smash{\raisebox{0.6em}{size}} 
& \hspace{0.5em}mean\hspace{0.5em} & deviation 
& \hspace{0.5em}mean\hspace{0.5em} & deviation \\ \hline
$2$ & $\phantom{2}{-}3.0$& $5$ & $-1.5$ & $1.4$ \\% \hline
$3$& $\phantom{2}{-}9.4$& $11$ & $-2.3$ & $2.3$\\% \hline
$4$ & $-20\phantom{.4}$& $20$ & $-3.8$ & $3.1$\\ \hline
\end{tabular} 
\smallskip

{\small
Results for a sample of $2000$ instances}
\end{center}
\renewcommand{\arraystretch}{1}

\caption{Loss of precision for LU factorization}
\label{fig:LU}
\end{figure}
%
